---
title: "Daily Status 20170419"
author: "Jesse Leigh Patsolic"
output: 
  html_document:
    keep_md: true
---

```{r render, eval=FALSE, echo=FALSE}
require(reshape2)
require(gridExtra)
require(ggplot2)
require(rmarkdown)
rmarkdown::render("miniReport.Rmd")
system('open miniReport.html')
```

## Accomplishments 
- ran meda time tests
- started on ROC curves

```{r c1, echo = FALSE}
load("~/neurodata/meda/examples/tout.RData")
m <- as.matrix(tout)
rownames(m) <- NULL
d1 <- data.frame(m)
m1 <- cbind(melt(d1), sampleSize = seq(1e3,1e4,by = 1e3))
```

## MEDA timing plots run on MARCC

```{r timePlots, fig.height = 8}
gg1 <- ggplot(m1, aes(x = sampleSize, y = value, color = variable)) +
  scale_x_continuous(breaks = seq(1e3,1e4,1e3)) +
  geom_point() + 
  geom_line()

gg2 <- ggplot(m1, aes(x = sampleSize, y = value, color = variable)) +
  scale_x_continuous(breaks = seq(1e3,1e4,1e3)) +
  scale_y_log10() + 
  geom_point() + 
  geom_line() + 
  ggtitle("Log10 scale")

grid.arrange(gg1, gg2)
```


### [ROC Curves for IB and IHC](./ROC.html)
NB: the plots I showed in my office weren't exactly right, I forgot to
split up the different response variables after melting the data.frame.

## Next Steps
- ROC Images for NeuroMab data
- nicely formatted plots for meda (html or rmarkdown) just for showing
  plots not for doing any computing.



